Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-12-10 docs/00-manuscripts/ieee/ieee-manuscript.tex
add funding info
add table with all vegindex references

@@

	%\setlength{\itemsep}{-\parsep}

	\acro{AGB}{above-ground biomass}
	\acro{ALE}{accumulated local effects}
	\acro{ALS}{airborne laser scanning}
	\acro{ANN}{artificial neural network}
	\acro{AUROC}{area under the receiver operating characteristics curve}
	\acro{BRT}{boosted regression trees}
	\acro{CART}{classification and regression trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{environmental niche modeling}
	\acro{FPR}{false positive rate}
	\acro{FFS}{forward feature selection}
	\acro{FS}{feature selection}
	\acro{GAM}{generalized additive model}
	\acro{GBM}{gradient boosting machine}
	\acro{GLM}{generalized linear model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{interquartile range}
	\acro{MARS}{multivariate adaptive regression splines}
	\acro{MBO}{model-based optimization}
	\acro{MEM}{maximum entropy model}
	\acro{ML}{machine learning}
	\acro{NDII}{normalized difference infrared index}
	\acro{NIR}{near-infrared}
	\acro{NRI}{normalized ratio index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{locally weighted scatter plot smoothing}
	\acro{PISR}{potential incoming solar radiation}
	\acro{PCA}{principal component analysis}
	\acro{PDP}{partial dependence plots}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{radial basis function}
	\acro{RF}{random forest}
	\acro{RMSE}{root mean square error}
	\acro{RR}{ridge regression}
	\acro{RSS}{residual sum of squares}
	\acro{SAR}{synthetic aperture radar}
	\acro{SDM}{species distribution modeling}
	\acro{SMBO}{sequential-based model optimization}
	\acro{SVM}{support vector machine}
	\acro{TPR}{true positive rate}
	\acro{VI}{vegetation index}
	\acro{XGBoost}{extreme gradient boosting}
\end{acronym}
\renewcommand{\IEEEiedlistdecl}{\relax}% reset back

@@

\begin{figure} [t!]
	\begin{center}
		\centering
		\includegraphics[width=0.48\textwidth] {study-area-hyperspectral.pdf}
		\caption{Information about location, size and spatial distribution of trees for all plots used in this study.}\label{fig:study_area}
	\end{center}
\end{figure}

@@

@@

% parameter limits
\begin{table}[b!]
\centering
\caption[t]{Hyperparameter ranges and types for each model.
	Hyperparameter notations from the respective R packages were used.}
\begingroup\footnotesize
\begin{tabularx}{.5\textwidth}{llXXrXX}
	\\
	\specialcell{Model                                          \\ (package)}                & Hyperparameter              & Type    & Start     & End      & Default \\
	\toprule
	\multirow{3}{*}{\specialcell{RF                                 \\ (ranger)}}       & \texttt{$x_try$}    & dbl & 0         & 0.5      & -       \\
	 & \texttt{min.node.size}      & int & 1        & 10      & 1   \\
	 & \texttt{sample.fraction}    & dbl & 0.2      & 0.9     & 1   \\
	\midrule
	\multirow{2}{*}{\specialcell{SVM                                \\ (kernlab)}}     & \texttt{C}                  & dbl & $2^{-10}$ & $2^{10}$ & 1       \\
	 & \texttt{$\sigma$}           & dbl & $2^{-5}$ & $2^{5}$ & 1   \\
	\midrule
	\multirow{7}{*}{\specialcell{XGBoost                            \\ (xgboost)}} & \texttt{nrounds}            & int & 10        & 600      & -       \\
	 & \texttt{colsample\_bytree}  & dbl & 0.3      & 0.7     & 1   \\
	 & \texttt{subsample}          & dbl & 0.25     & 1       & 1   \\
	 & \texttt{max\_depth}         & int & 1        & 10      & 6   \\
	 & \texttt{gamma}              & int & 0        & 10      & 0   \\
	 & \texttt{eta}                & dbl & 0.01     & 0.6     & 0.3 \\
	 & \texttt{min\_child\_weight} & int & 0        & 20      & 1   \\
	\bottomrule
\end{tabularx}
\endgroup
\label{tab:hyperparameter_limits}
\end{table}

>>>>

\usepackage{xtab}

@@

	%\setlength{\itemsep}{-\parsep}
	\acro{AGB}{above-ground biomass}
	\acro{ALE}{accumulated local effects}
	\acro{ALS}{airborne laser scanning}
	\acro{ANN}{artificial neural network}
	\acro{AUROC}{area under the receiver operating characteristics curve}
	\acro{BRT}{boosted regression trees}
	\acro{CART}{classification and regression trees}
	\acro{CNN}{convolutional neural networks}
	\acro{CV}{cross-validation}
	\acro{DAP}{digital aerial photogrammetry}
	\acro{ENM}{environmental niche modeling}
	\acro{FPR}{false positive rate}
	\acro{FFS}{forward feature selection}
	\acro{FS}{feature selection}
	\acro{GAM}{generalized additive model}
	\acro{GBM}{gradient boosting machine}
	\acro{GLM}{generalized linear model}
	\acro{ICGC}{Institut Cartografic i Geologic de Catalunya}
	\acro{IQR}{interquartile range}
	\acro{MARS}{multivariate adaptive regression splines}
	\acro{MBO}{model-based optimization}
	\acro{MEM}{maximum entropy model}
	\acro{ML}{machine learning}
	\acro{NDII}{normalized difference infrared index}
	\acro{NIR}{near-infrared}
	\acro{NRI}{normalized ratio index}
	\acro{OLS}{ordinary least squares}
	\acro{LiDAR}{light detection and ranging}
	\acro{LOWESS}{locally weighted scatter plot smoothing}
	\acro{PISR}{potential incoming solar radiation}
	\acro{PCA}{principal component analysis}
	\acro{PDP}{partial dependence plots}
	\acro{PLS}{partial least-squares}
	\acro{RBF}{radial basis function}
	\acro{RF}{random forest}
	\acro{RMSE}{root mean square error}
	\acro{RR}{ridge regression}
	\acro{RSS}{residual sum of squares}
	\acro{SAR}{synthetic aperture radar}
	\acro{SDM}{species distribution modeling}
	\acro{SMBO}{sequential-based model optimization}
	\acro{SVM}{support vector machine}
	\acro{TPR}{true positive rate}
	\acro{VI}{vegetation index}
	\acro{XGBoost}{extreme gradient boosting}
\end{acronym}
\renewcommand{\IEEEiedlistdecl}{\relax}% reset back

@@

% \begin{figure} [t!]
% 	\begin{center}
% 		\centering
% 		\includegraphics[width=0.48\textwidth] {study-area-hyperspectral.pdf}
% 		\caption{Information about location, size and spatial distribution of trees for all plots used in this study.}\label{fig:study_area}
% 	\end{center}
% \end{figure}

@@

\section{Acknowledgments}
This work was funded by the EU LIFE Healthy Forest project (LIFE14 ENV/ES/000179) and the German Scholars Organization/Carl Zeiss Foundation.

@@

% parameter limits
\begin{table}[b!]
	\centering
	\caption[t]{Hyperparameter ranges and types for each model.
		Hyperparameter notations from the respective R packages were used.}
	\begingroup\scriptsize
	\begin{tabularx}{.5\textwidth}{llXXrXX}
		\\
		\specialcell{Model                                              \\ (package)}                & Hyperparameter              & Type    & Start     & End      & Default \\
		\toprule
		\multirow{3}{*}{\specialcell{RF                                 \\ (ranger)}}       & \texttt{$x_try$}    & dbl & 0         & 0.5      & -       \\
		 & \texttt{min.node.size}      & int & 1        & 10      & 1   \\
		 & \texttt{sample.fraction}    & dbl & 0.2      & 0.9     & 1   \\
		\midrule
		\multirow{2}{*}{\specialcell{SVM                                \\ (kernlab)}}     & \texttt{C}                  & dbl & $2^{-10}$ & $2^{10}$ & 1       \\
		 & \texttt{$\sigma$}           & dbl & $2^{-5}$ & $2^{5}$ & 1   \\
		\midrule
		\multirow{7}{*}{\specialcell{XGBoost                            \\ (xgboost)}} & \texttt{nrounds}            & int & 10        & 600      & -       \\
		 & \texttt{colsample\_bytree}  & dbl & 0.3      & 0.7     & 1   \\
		 & \texttt{subsample}          & dbl & 0.25     & 1       & 1   \\
		 & \texttt{max\_depth}         & int & 1        & 10      & 6   \\
		 & \texttt{gamma}              & int & 0        & 10      & 0   \\
		 & \texttt{eta}                & dbl & 0.01     & 0.6     & 0.3 \\
		 & \texttt{min\_child\_weight} & int & 0        & 20      & 1   \\
		\bottomrule
	\end{tabularx}
	\endgroup
	\label{tab:hyperparameter_limits}
\end{table}

\begingroup\scriptsize
\setlength\tabcolsep{4pt}  % default value: 6pt
\begin{xtabular*}{0.3\textwidth}{lll}
	\bfseries{Name} & \bfseries{Formula}                                                                                  & \bfseries{Reference*}      \\
	Boochs          & $D_{703}$                                                                                           & \cite{boochs1990}       \\
	Boochs2         & $D_{720}$                                                                                           & \cite{boochs1990}       \\
	CAI             & $0.5 \times (R_{2000} + R_{2200}) -R_{2100}$                                                        & \cite{nagler2003}       \\
	\midrule
	CARI            & $a = (R_{700}-R_{550}) / 150$                                                                       & \cite{walthall1994}          \\
	& $b = R_{550}-(a\times 550)$                                                                                         &                                  \\
	& $\frac{R_{700}\times | (a\times 670+R_{670}+b)}{R_{670}\times(a^2+1)| ^{0.5}}$                                      &                                  \\
	\midrule
	Carter          & $R_{695}/R_{420}$                                                                                   & \cite{carter1994}              \\
	Carter2         & $R_{695}/R_{760}$                                                                                   & \cite{carter1994}              \\
	Carter3         & $R_{605}/R_{760}$                                                                                   & \cite{carter1994}              \\
	Carter4         & $R_{710}/R_{760}$                                                                                   & \cite{carter1994}              \\
	Carter5         & $R_{695}/R_{670}$                                                                                   & \cite{carter1994}              \\
	Carter6         & $R_{550}$                                                                                           & \cite{carter1994}              \\
	CI              & $R_{675}\times R_{690}/R_{683}^2$                                                                   & \cite{zarco-tejada2003a} \\
	CI2             & $R_{760}/R_{700}-1$                                                                                 & \cite{gitelson2003}     \\
	ClAInt          & $\int_{600 nm}^{735 nm} R$                                                                          & \cite{oppelt2004}   \\
	CRI1            & $1/R_{515}-1/R_{550}$                                                                               & \cite{gitelson2003}     \\
	CRI2            & $1/R_{515}-1/R_{770}$                                                                               & \cite{gitelson2003}     \\
	CRI3            & $1/R_{515}-1/R_{550}\times R_{770}$                                                                 & \cite{gitelson2003}     \\
	CRI4            & $1/R_{515}-1/R_{700}\times R_{770}$                                                                 & \cite{gitelson2003}     \\
	D1              & $D_{730}/D_{706}$                                                                                   & \cite{zarco-tejada2003a} \\
	D2              & $D_{705}/D_{722}$                                                                                   & \cite{zarco-tejada2003a} \\
	Datt            & $(R_{850}-R_{710})/(R_{850}-R_{680})$                                                               & \cite{datt1999}               \\
	Datt2           & $R_{850}/R_{710}$                                                                                   & \cite{datt1999}               \\
	Datt3           & $D_{754}/D_{704}$                                                                                   & \cite{datt1999}               \\
	Datt4           & $R_{672}/(R_{550} \times R_{708})$                                                                  & \cite{datt1998}                \\
	Datt5           & $R_{672}/R_{550}$                                                                                   & \cite{datt1998}                \\
	Datt6           & $(R_{860})/(R_{550}\times R_{708})$                                                                 & \cite{datt1998}                \\
	Datt7           & $(R_{860} - R_{2218})/(R_{860} - R_{1928})$                                                         & \cite{datt1999a}               \\
	Datt8           & $(R_{860} - R_{1788})/(R_{860} - R_{1928})$                                                         & \cite{datt1999a}               \\
	DD              & $(R_{749}-R_{720})-(R_{701}-R_{672})$                                                               & \cite{maire2004}     \\
	DDn             & $2\times (R_{710}-R_{660}-R_{760})$                                                                 & \cite{lemaire2008}     \\
	DPI             & $(D_{688}*D_{710})/D_{697}^2$                                                                       & \cite{zarco-tejada2003a} \\
	DWSI1           & $R_{80}/R_{1660}$                                                                                   & \cite{apan2004}         \\
	DWSI2           & $R_{1660}/R_{550}$                                                                                  & \cite{apan2004}         \\
	DWSI3           & $R_{1660}/R_{680}$                                                                                  & \cite{apan2004}         \\
	DWSI4           & $R_{550}/R_{680}$                                                                                   & \cite{apan2004}         \\
	DWSI5           & $(R_{800} + R_{550})/(R_{1660} + R_{680})$                                                          & \cite{apan2004}         \\
	EGFN            & $\frac{(\max(D_{650:750})-\max(D_{500:550}))}{(\max(D_{650:750})+\max(D_{500:550}))}$               & \cite{penuelas1994}     \\
	EGFR            & $\max(D_{650:750})/\max(D_{500:550})$                                                               & \cite{penuelas1994}     \\
	EVI             & $\frac{2.5\times ((R_{800}-R_{670}) }{ (R_{800}-(6\times R_{670})-(7.5\times R_{475})+1)}$          & \cite{huete1997a}        \\
	GDVI            & $(R_{800}^n-R_{680}^n) / (R_{800}^n+R_{680}^n)$**                                                   & \cite{wu2014}                  \\
	GI              & $R_{554}/R_{677}$                                                                                   & \cite{smith1995}        \\
	Gitelson        & $1/R_{700}$                                                                                         & \cite{gitelson1999}     \\
	Gitelson2       & $(R_{750}-R_{800}/R_{695}-R_{740})-1$                                                               & \cite{gitelson2003}   \\
	GMI1            & $R_{750}/R_{550}$                                                                                   & \cite{gitelson2003}     \\
	GMI2            & $R_{750}/R_{700}$                                                                                   & \cite{gitelson2003}     \\
	Green NDVI      & $\frac{R_{800}-R_{550}}{R_{800}+R_{550}}$                                                           & \cite{gitelson1996}     \\
	LWVI\_1         & $\frac{(R_{1094}-R_{983})}{(R_{1094}+R_{983})}$                                                     & \cite{galvao2005}       \\
	LWVI\_2         & $\frac{R_{1094}-R_{1205}}{R_{1094}+R_{1205}}$                                                       & \cite{galvao2005}       \\
	Maccioni        & $\frac{R_{780}-R_{710})}{R_{780}-R_{680}}$                                                          & \cite{maccioni2001}     \\
	\midrule
	MCARI           & \parbox{5.5cm}{$((R_{700}-R_{670})-0.2\times (R_{700}-R_{550})) \times (R_{700}/R_{670})$}          & \cite{daughtry2000}     \\
	\midrule
	MCARI2          & \parbox{5.5cm}{$((R_{750}-R_{705})-0.2 \times (R_{750}-R_{550})) \times (R_{750}/R_{705})$}         & \cite{wu2008a}           \\
	\midrule
	mND705          & $\frac{(R_{750}-R_{705})}{R_{750}+R_{705}-2\times R_{445}}$ & \cite{sims2002a} \\
	mNDVI           &  $\frac{(R_{800}-R_{680})}{R_{800}+R_{680}-2 \times R_{445}}$ & \cite{sims2002a} \\
	MPRI            & $\frac{R_{515}-R_{530}}{R_{515}+R_{530}}$                                                           & \cite{hernandez-clemente2011}\\
	MSAVI           & \parbox{5.5cm}{$0.5 \times ((2\times R_{800}+1)^2-8\times (R_{800}-R_{670}))^{0.5}$}                & \cite{qi1994}\\
	MSI             & $\frac{R_{1600}}{R_{817}}$                                                                          & \cite{huntjr1989}\\
	mSR             & $\frac{R_{800}-R_{445}}{R_{680}-R_{445}}$                                                           & \cite{sims2002a} \\
	mSR2            & $\frac{(R_{750}/R_{705})-1}{R_{750}/R_{705}+1)^{0.5}}$                                              & \cite{chen1996}\\
	mSR705          & $\frac{R_{750}-R_{445}}{R_{705}-R_{445}}$                                                           & \cite{sims2002a} \\
	MTCI            & $\frac{R_{754}-R_{709}}{R_{709}-R_{681}}$                                                           & \cite{dash2007}\\
	\midrule
	MTVI            & \parbox{3.8cm}{$1.2 \times (1.2 \times (R_{800}-R_{550})-2.5 \times (R_{670}-R_{550}))$}            & \cite{haboudane2002}\\
	\midrule
	NDLI           & $\frac{log(1/R_{1754}) - log(1/R_{1680})}{log(1/R_{1754}) + log(1/R_{1680})}$                        & \cite{serrano2002} \\
	NDNI           & $\frac{log(1/R_{1510}) - log(1/R_{1680})}{log(1/R_{1510}) + log(1/R_{1680})}$                        & \cite{serrano2002} \\
	NDVI           & $\frac{R_{800}-R_{680}}{R_{800}+R_{680}}$                                                            & \cite{tucker1979} \\
	NDVI2          & $\frac{R_{750}-R_{705}}{R_{750}+R_{705}}$                                                            & \cite{gitelson1994} \\
	NDVI3          & $\frac{R_{682}-R_{553}}{R_{682}+R_{553}}$                                                            & \cite{guanter2005} \\
	NDWI           & $\frac{R_{860}-R_{1240}}{R_{860}+R_{1240}}$                                                          & \cite{gao1996} \\
	NPCI           & $\frac{R_{680}-R_{430}}{R_{680}+R_{430}}$                                                            & \cite{penuelas1994} \\
	OSAVI          & $\frac{(1+0.16) \times (R_{800}-R_{670})}{R_{800}+R_{670}+0.16 }$                                    & \cite{rondeaux1996} \\
	OSAVI2         & $\frac{(1+0.16)\times (R_{750}-R_{705})}{R_{750}+R_{705}+0.16) }$                                    & \cite{wu2008a} \\
	PARS           & $\frac{R_{746}}{R_{513}}$                                                                            & \cite{chappelle1992} \\
	PRI            & $\frac{R_{531}-R_{570}}{R_{531}+R_{570}}$                                                            & \cite{gamon1992}\\
	PRI\_norm      & $\frac{PRI \times (-1) }{RDVI\times R_{700}/R_{670}}$                                                & \cite{zarco-tejada2013a}\\
	PRI*CI2        & $PRI*CI2$                                                                                            & \cite{garrity2011} \\
	PSRI           & $\frac{R_{678}-R_{500}}{R_{750}}$                                                                    & \cite{merzlyak1999} \\
	PSSR           & $\frac{R_{800}}{R_{635}}$                                                                            & \cite{blackburn1998} \\
	PSND           & $\frac{R_{800}-R_{470}}{R_{800}-R_{470})}$                                                           & \cite{blackburn1998} \\
	PWI            & $\frac{R_{900}}{R_{970}}$                                                                            & \cite{penuelas1997} \\
	RDVI           & $\frac{R_{800}-R_{670}}{ \sqrt{R_{800}+R_{670}}}$                                                    & \cite{roujean1995} \\
	\midrule
	REP\_LE        & \parbox{3.8cm}{Red-edge position through linear extrapolation}                                       & \cite{cho2006} \\
	\midrule
	REP\_Li        & $R_{re}=\frac{R_{670}+R_{780})}{2}$                                                                  & \cite{guyot1988} \\
	& $\frac{700 + 40 \times ((R_{re} -R_{700})}{(R_{740}-R_{700}))}$ & \\
	\midrule
	SAVI           & $\frac{(1+L)\times (R_{800}-R_{670})}{(R_{800}+R_{670}+L)}$                                          & \cite{huete1988} \\
	SIPI           & $\frac{R_{800}-R_{445}}{R_{800}-R_{680}}$                                                            & \cite{pen-uelas1995} \\
	\midrule
	SPVI           & \parbox{3.8cm}{$0.4 \times 3.7 \times (R_{800}-R_{670})-1.2 \times ((R_{530}-R_{670})^2)^{0.5}$}     & \cite{vincini2006} \\
	\midrule
	SR             & $\frac{R_{800}}{R_{680}}$                                                                            & \cite{jordan1969} \\
	SR1            & $\frac{R_{750}}{R_{700}}$                                                                            & \cite{gitelson1997}\\
	SR2            & $\frac{R_{752}}{R_{690}}$                                                                            & \cite{gitelson1997}\\
	SR3            & $\frac{R_{750}}{R_{550}}$                                                                            & \cite{gitelson1997}\\
	SR4            & $\frac{R_{700}}{R_{670}}$                                                                            & \cite{mcmurtrey1994} \\
	SR5            & $\frac{R_{675}}{R_{700}}$                                                                            & \cite{chappelle1992} \\
	SR6            & $\frac{R_{750}}{R_{710}}$                                                                            & \cite{zarco-tejada1999} \\
	SR7            & $\frac{R_{440}}{R_{690}}$                                                                            & \cite{lichtenthaler1996} \\
	SR8            & $\frac{R_{515}}{R_{550}}$                                                                            & \cite{hernandez-clemente2012}\\
	SRPI           & $\frac{R_{430}}{R_{680}}$                                                                            & \cite{pen-uelas1995}\\
	SRWI           & $\frac{R_{850}}{R_{1240}}$                                                                           & \cite{zarco-tejada2003a}\\
	Sum\_Dr1       & $\sum_{i=626}^{795} D1_i$                                                                            & \cite{elvidge1995} \\
	Sum\_Dr2       & $\sum_{i=680}^{780} D1_i$                                                                            & \cite{filella1994} \\
	SWIR FI        & $\frac{R_{2133}^2}{R_{2225} \times R_{2209}^3}$                                                      & \cite{levin2007} \\
	\midrule
	SWIR LI        & \parbox{3.8cm}{$3.87  \times (R_{2210} - R_{2090}) - 27.51 \times (R_{2280} - R_{2090}) - 0.2$}      & \cite{lobell2001} \\
	\midrule
	SWIR SI        & \parbox{3.8cm}{$-41.59 \times (R_{2210} - R_{2090}) + 1.24 \times (R_{2280} - R_{2090}) + 0.64 $}    & \cite{lobell2001} \\
	\midrule
	SWIR VI        & \parbox{3.8cm}{$37.72  \times (R_{2210} - R_{2090}) + 6.27 \times (R_{2280} - R_{2090}) + 0.57$}     & \cite{lobell2001} \\
	\midrule
	TCARI          & \parbox{3.8cm}{$3*((R_{700}-R_{670})-0.2\times R_{700}-R_{550})\times (R_{700}/R_{670}))$}           & \cite{haboudane2002} \\
	\midrule
	TCARI/OSAVI    & TCARI/OSAVI                                                                                          & \cite{haboudane2002} \\
	\midrule
	TCARI2         & \parbox{3.8cm}{$3 \times ((R_{750}-R_{705})-0.2 \times (R_{750}-R_{550}) \times (R_{750}/R_{705}))$} & \cite{wu2008a} \\
	\midrule
	TCARI2/OSAVI2  & TCARI2/OSAVI2                                                                                        & \cite{wu2008a} \\
	\midrule
	TGI            & \parbox{3.8cm}{$-0.5 (190 (R_{670} - R_{550} ) - 120 (R_{670} - R_{480}))$}                          & \cite{hunt2013} \\
	\midrule
	TVI            &\parbox{3.8cm}{$0.5\times (120 \times (R_{750}-R_{550})-200 \times (R_{670}-R_{550}))$}               & \cite{broge2001} \\
	\midrule
	Vogelmann      & $\frac{R_{740}}{R_{720}}$                                                                            & \cite{vogelmann1993} \\
	Vogelmann2     & $\frac{R_{734}-R_{747}}{R_{715}+R_{726})}$                                                           & \cite{vogelmann1993} \\
	Vogelmann3     & $\frac{D_{715}}{D_{705}}$                                                                            & \cite{vogelmann1993} \\
	Vogelmann4     & $\frac{R_{734}-R_{747}}{R_{715}+R_{720}}$                                                            & \cite{vogelmann1993} \\
\end{xtabular*}
\endgroup
